### 2015-09-21 bioc192/lect31.tex
finished lecture 31, onto lecture 32

>>>>

\subsection{Rotenone}

Rotenone inhibits electron transfer from complex I to coenzyme Q

\subsection{Cyanide}

Cyanide binds to cytochrome a3, which is in complex IV.

\subsection{Carbon Monoxide}

Carbon monoxide binds to where oxygen binds on complex IV, and therefore prevents the electron transfer.

\subsection{Consequences}

All of these will stop the electrons from flowing through the ETC.
This will in turn prevent the oxidation of NADH and FADH$_2$, which means that these co-enzymes cannot get recycled back into its oxidised form (NAD$^+$ and FAD).
If there are no NAD$^+$ or FAD around, $\beta$-oxidation and citric acid cycle shuts down as well.
As a result, protons don't get pumped and therefore no (or decreased) ATP produced.
Reactive oxygen species can also be produced when the ETC is inhibited, as the electrons have to be passed onto somewhere.
Since this transfer is from another complex, the electron transfer is incomplete and results in the production of highly damaging reactive oxygen species.
